Analysis of the \\ Information Security Job Landscape \\ in Austria

### 2020-05-29 paper/paper.tex
Fix spelling.

The next two obvious education types were the bachelor's and master's degree. For these, we again simply checked if any word contains the respective term and categorise them accordingly. Another related education type is an FH (Fachhochschule) degree which can be equivalent to either a bachelor's or master's degree. Here we again took the same approach as for the \texttt{matura} category, since both “\german{FH-Abschluss}” and “\german{Fachhochschulabschluss}” are commonly used terms.

@@

In comparison to the other extraction tasks, extracting certifications was straight-forward given this fixed list. There was, however, still one adjustment needed for the data cleaning step with regards to the ISO/IEC certifications since some of them only specified \texttt{'ISO'} while others specified \texttt{'ISO/IEC'}. A few of them were also missing whitespace between the acronym and the number, e.g. \texttt{'ISO27001'}. For this reason, we added another regular expression replacement to the data cleaning step which normalises all of these occurrences to the canonical \texttt{'ISO/IEC~\#\#\#\#\#'} form.

>>>>

The next two obvious education types were the bachelor's and master's degree. For these, we again simply checked if any word contains the respective term and categorise them accordingly. Another related education type is an \german{FH} (\german{Fachhochschule}) degree which can be equivalent to either a bachelor's or master's degree. Here we again took the same approach as for the \texttt{matura} category, since both “\german{FH-Abschluss}” and “\german{Fachhochschulabschluss}” are commonly used terms.

@@

In comparison to the other extraction tasks, extracting certifications was straight-forward given this fixed list. There was, however, still one adjustment needed for the data cleaning step with regards to the ISO/IEC certifications since some of them only specified \texttt{'ISO'} while others specified \texttt{'ISO/IEC'}. A few of them were also missing white space between the acronym and the number, e.g. \texttt{'ISO27001'}. For this reason, we added another regular expression replacement to the data cleaning step which normalises all of these occurrences to the canonical \texttt{'ISO/IEC~\#\#\#\#\#'} form.
